Tracing R Base: +

### 2019-04-25 notebooks/rplus.Rmd
small fix

subtype_df_L0_p <- filter(subtype_df_L0, fun == "+")
subtype_df_L1_p <- filter(subtype_df_L1, fun == "+")
subtype_df_L2_p <- filter(subtype_df_L2, fun == "+")

>>>>

subtype_df_L0_p <- filter(subtype_df_L0, fun == "+") %>% salient_only_one_fun
subtype_df_L1_p <- filter(subtype_df_L1, fun == "+") %>% salient_only_one_fun
subtype_df_L2_p <- filter(subtype_df_L2, fun == "+") %>% salient_only_one_fun(just_types=F)
